moduleoneanalysis

### 2023-09-20 module1/moduleoneanalysis.Rmd
modificationd for better pdf output

```{r load packages, warning = FALSE, message = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(psych))

@@

colnames(codedmodule1)
addedcols <- codedmodule1 %>%
  mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet, house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty, food1, food2, food3, food4, foodadequacy, foodtrouble, illness, severeillness, Llenght, Lfarmbigha, Lanimalcowbull, Lanimalcattle, Lanimalhorses, Lanimalgoats, Lanimalsheep, Lanimalpoultry, Ilenght, Ipropvalue, farwatermins, healthdist), as.numeric) %>%
  mutate(stove = cook1 + cook2 + cook3 + cook4, 
        vehicle = vehicle1 + vehicle2 + vehicle3 + vehicle4 + vehicletext,
        food = food1 + food2 + food3 + food4,
        #income = totalincome + otherincome,
        animals = Lanimalcowbull + Lanimalcattle + Lanimalhorses + Lanimalgoats + Lanimalsheep + Lanimalpoultry) %>%
  dplyr::select(-cook1, -cook2, -cook3, -cook4, -vehicle1, -vehicle2, -vehicle3, -vehicle4, -vehicletext, -food1, -food2, -food3, -food4, -Lanimalcowbull, -Lanimalcattle, -Lanimalhorses, -Lanimalgoats, -Lanimalsheep, -Lanimalpoultry) %>%
  unite("LIlenght", c(Llenght,Ilenght), na.rm = TRUE, remove = TRUE)%>%
  unite("LIassociation", c(Lassociation,Iassociation), na.rm = TRUE, remove = TRUE)

@@

codedmodule1 %>% count(Livelihood_Income)
addedcols %>% count(Livelihood_Income)
codedmodule1 %>% count(Lfarmbigha)
codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
codedmodule1 %>% count(Lboat)

addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)

addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)

@@

module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)

@@

str(nuclear_LI)

@@

summary(nuclearLI_lm)
summary(nuclearLI_lm2)
#plot(nuclearLI_lm)

@@

# Displaying the first few rows of the dataframe
head(solar_LI)

@@

solarLI_lm2 <- lm(Risky_Solar ~ caste + gender + urban_rural + LIscore , data = solar_model)
summary(solarLI_lm)
summary(solarLI_lm2)
#plot(solarLI_lm)

@@

summary(coalLI_lm)
summary(coalLI_lm2)
#plot(coalLI_lm)

@@

# Print the summary of the CFA results, including fit measures
summary(JIS_cfa, fit.measure= TRUE, standardized = TRUE)

@@

summary(JIS_lm1)

@@

@@

#Extra

##checking stuff
codedmodule1

codedmodule1 %>%
  filter(Livelihood_Income == "LSI") %>%
  count(Lfarmland)
codedmodule1 %>%
  count(Iproperty)

lapply(codedmodule1, unique)
ncol(codedmodule1)
colnames(codedmodule1)

str(codedmodule1)

>>>>

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(psych))

@@

addedcols <- codedmodule1 %>%
  mutate_at(vars(Lassociation, Lboat, Iassociation, totalincome, otherincome, govtscheme, education, subsidyknow, drinkingwater, cookingwater, wateravail, toilet, house, houseown, cook1, cook2, cook3, cook4, vehicle1, vehicle2, vehicle3, vehicle4, vehicletext, polposition, polparty, food1, food2, food3, food4, foodadequacy, foodtrouble, illness, severeillness, Llenght, Lfarmbigha, Lanimalcowbull, Lanimalcattle, Lanimalhorses, Lanimalgoats, Lanimalsheep, Lanimalpoultry, Ilenght, Ipropvalue, farwatermins, healthdist), as.numeric) %>%
  mutate(stove = cook1 + cook2 + cook3 + cook4, 
        vehicle = vehicle1 + vehicle2 + vehicle3 + vehicle4 + vehicletext,
        food = food1 + food2 + food3 + food4,
        #income = totalincome + otherincome,
        animals = Lanimalcowbull + Lanimalcattle + Lanimalhorses + Lanimalgoats + Lanimalsheep + Lanimalpoultry) %>%
  dplyr::select(-cook1, -cook2, -cook3, -cook4, -vehicle1, -vehicle2, -vehicle3, -vehicle4, -vehicletext, -food1, -food2, -food3, -food4, -Lanimalcowbull, -Lanimalcattle, -Lanimalhorses, -Lanimalgoats, -Lanimalsheep, -Lanimalpoultry) %>%
  unite("LIlenght", c(Llenght,Ilenght), na.rm = TRUE, remove = TRUE)%>%
  unite("LIassociation", c(Lassociation,Iassociation), na.rm = TRUE, remove = TRUE)

@@

#codedmodule1 %>% count(Livelihood_Income)
#addedcols %>% count(Livelihood_Income)
#codedmodule1 %>% count(Lfarmbigha)
#codedmodule1 %>% filter(Livelihood_Income == "LSI") %>% count(Lfarmland)
#addedcols %>% filter(Livelihood_Income == "LSI") %>% count(animals)
#codedmodule1 %>% count(Lboat)

#addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(Lboat)
#addedcols %>% filter(Livelihood_Income == "LSI") %>% filter(Lfarmland == "Doesn't apply") %>% count(animals)

#addedcols %>% filter(Livelihood_Income == "ISI") %>% count(Iproperty)

@@

#module1 %>% filter(!row_number() %in% c(1,2)) %>% filter(Livelihood_Income != "(a) own farming/fishing/animal rearing/business") %>% count(Iproperty)

@@

@@

#plot(nuclearLI_lm)

@@

# Displaying the first few rows of the dataframe

@@

solarLI_lm2 <- lm(Risky_Solar ~ caste + gender + urban_rural + LIscore , data = solar_model)
#plot(solarLI_lm)

@@

#plot(coalLI_lm)

@@

# Print the summary of the CFA results, including fit measures
#summary(JIS_cfa, fit.measure= TRUE, standardized = TRUE)

@@

@@

##checking stuff

#codedmodule1 %>%
  #filter(Livelihood_Income == "LSI") %>%
  #count(Lfarmland)
#codedmodule1 %>%
  #count(Iproperty)

#lapply(codedmodule1, unique)

#str(codedmodule1)

@@
